raptr: Representative and Adequate Prioritization Toolkit in R

### 2016-11-28 code/rmarkdown/article.Rmd
+ add spaces after tweetable abstract for new line
+ add spaces after short title
+ move abstract onto seperate page

---
title: "raptr: Representative and Adequate Prioritization Toolkit in R"
author: |
  | Jeffrey O. Hanson$^1$, Jonathan R. Rhodes$^2$, Hugh P. Possingham$^{1,3}$, Richard A. Fuller$^1$
  | $^1$School of Biological Sciences, The University of Queensland, Brisbane, QLD, Australia
  | $^2$School of Geography, Planning and Environmental Management, The University of Queensland, Brisbane, QLD, Australia
  | $^3$The Nature Conservancy, South Brisbane, QLD, Australia
  | Correspondance should be addressed to jeffrey.hanson@uqconnect.edu.au
date: "`r format(Sys.time(), '%d %B %Y')`"
tags: ["conservation", "biodiversity", "MILP", "reserve-selection", "optimization", "protected area"]
abstract: "
1. An underlying aim in conservation planning is to maximize the long-term persistence of biodiversity. To fulfill this aim, the ecological and evolutionary processes that sustain biodiversity must be preserved. One way to conserve such processes at the feature level (eg. species, ecosystem) is to preserve a representative sample of the physical attributes that underpin them across the feature's geographic distribution. For example, the long-term persistence of a species may depend on its ability to adapt to new climatic conditions. By conserving individuals with the ability to persist in a range of conditions--physical attributes associated with adaptation--protected areas can foster evolutionary processes. Despite this, current reserve selection methods overwhelmingly focus on securing an adequate proportion of features' geographic ranges and little attention has been directed towards capturing a representative sample.

2. To address this issue, we developed the \\texttt{raptr R} package to guide reserve selection using targets for representing spatially explicit variables that underpin biodiversity processes as well as more typical area protection targets. Users set \"amount targets\"--similar to conventional methods--to secure a sufficient proportion of the features' geographic distributions. Additionally, users set \"space targets\" to secure a representative sample of variation in ecologically or evolutionary relevant attributes (eg. climatic or genetic variation). We demonstrate the functionality of this package using simulations and two case studies. We generate solutions using just amount targets--representing conventional methods--and compare them with solutions generated using amount and space targets.

@@

4. The \\texttt{raptr R} package provides a toolkit for making spatial conservation prioritizations that secure an adequate and representative sample of features. By targeting representativeness, prioritizations may have a greater chance of achieving long-term biodiversity persistence.
"
output:
  rmarkdown::pdf_document:
    toc: false
    keep_tex: yes
    fig_caption: yes
    includes:
      in_header: preamble.tex
fontsize: 11pt
documentclass: article
subparagraph: true
bibliography: references.bib
csl: reference-style.csl
---

Short running title: Representative and adequate prioritizations  
Abstract word count: 346 / 350  
Total word count: 6974 / 7000  
Number of references: 42  
Number of figures: 8  
Number of tables: 0  
Number of textboxes: 0  
Number of equations: 4

>>>>

---
title: "raptr: Representative and Adequate Prioritization Toolkit in R"
author: |
  | Jeffrey O. Hanson$^1$, Jonathan R. Rhodes$^2$, Hugh P. Possingham$^{1,3}$, Richard A. Fuller$^1$
  | $^1$School of Biological Sciences, The University of Queensland, Brisbane, QLD, Australia
  | $^2$School of Geography, Planning and Environmental Management, The University of Queensland, Brisbane, QLD, Australia
  | $^3$The Nature Conservancy, South Brisbane, QLD, Australia
  | Correspondance should be addressed to jeffrey.hanson@uqconnect.edu.au
date: "`r format(Sys.time(), '%d %B %Y')`"
tags: ["conservation", "biodiversity", "MILP", "reserve-selection", "optimization", "protected area"]
output:
  rmarkdown::pdf_document:
    toc: false
    keep_tex: yes
    fig_caption: yes
    includes:
      in_header: preamble.tex
fontsize: 11pt
documentclass: article
subparagraph: true
bibliography: references.bib
csl: reference-style.csl
---

Short running title: Representative and adequate prioritizations  
Short abstract: Make smarter spatial conservation decisions that foster biodiversity processes using raptr R package  
Abstract word count: 346 / 350  
Total word count: 6974 / 7000  
Number of references: 42  
Number of figures: 8  
Number of tables: 0  
Number of textboxes: 0  
Number of equations: 4

\clearpage

1. An underlying aim in conservation planning is to maximize the long-term persistence of biodiversity. To fulfill this aim, the ecological and evolutionary processes that sustain biodiversity must be preserved. One way to conserve such processes at the feature level (eg. species, ecosystem) is to preserve a representative sample of the physical attributes that underpin them across the feature's geographic distribution. For example, the long-term persistence of a species may depend on its ability to adapt to new climatic conditions. By conserving individuals with the ability to persist in a range of conditions--physical attributes associated with adaptation--protected areas can foster evolutionary processes. Despite this, current reserve selection methods overwhelmingly focus on securing an adequate proportion of features' geographic ranges and little attention has been directed towards capturing a representative sample.

2. To address this issue, we developed the \\texttt{raptr R} package to guide reserve selection using targets for representing spatially explicit variables that underpin biodiversity processes as well as more typical area protection targets. Users set "amount targets"--similar to conventional methods--to secure a sufficient proportion of the features' geographic distributions. Additionally, users set "space targets" to secure a representative sample of variation in ecologically or evolutionary relevant attributes (eg. climatic or genetic variation). We demonstrate the functionality of this package using simulations and two case studies. We generate solutions using just amount targets--representing conventional methods--and compare them with solutions generated using amount and space targets.

@@

4. The \\texttt{raptr R} package provides a toolkit for making spatial conservation prioritizations that secure an adequate and representative sample of features. By targeting representativeness, prioritizations may have a greater chance of achieving long-term biodiversity persistence.
